---
title: 'Famat : determine functional links between metabolites and genes'
author: "Emilie Secherre"
package: famat
output: 
    BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{Vignette Title}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}  
---

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

# Introduction

The aim of `r Rpackage("famat")` is to allow users to determine functional links between metabolites and genes. These metabolites and genes lists may be related to a specific experiment/study, but `r Rpackage("famat")` only needs a gene symbols list and a Kegg Compound ids list. Using these lists, `r Rpackage("famat")` performs pathway enrichment analysis, direct interactions between elements inside pathways extraction, GO terms enrichment analysis, calculation of user's elements centrality (number of direct interactions between an element and others inside a pathway) and extraction of information related to user's elements. 

Functions available are :
- path_enrich : pathways enrichment analysis
- interactions : direct interactions and centrality
- compl_data : GO terms enrichment analysis and user's elements data extraction
- rshiny ; use of previous function's data in a shiny interface

# Installation

```{r load_famat}
BiocManager::install("famat")
library(famat)
```

